{\sc underworlds}: Cascading Situation Assessment for Robots

### 2017-09-27 paper.tex
Change template to use HRI one (ACM)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}

\usepackage{hyperref}

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
{\sc underworlds}: Cascading Situation Assessment for Robots
}

\author{Séverin Lemaignan$^{*}$, Fotios Papadopoulos$^{*}$%
\thanks{$^{*}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk}}%
}

@@

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[HRI2018]{ACM/IEEE Human-Robot Conference}{March 2018}{Chicago USA} 
\acmYear{2018}
\copyrightyear{2018}

\acmArticle{4}
\acmPrice{15.00}

\title{{\sc underworlds}: Cascading Situation Assessment for Robots
}

%\author{Séverin Lemaignan$^{*}$, Fotios Papadopoulos$^{*}$%
%\thanks{$^{*}$Authors are with Centre for Robotics and Neural Systems,
%        Plymouth University, Plymouth PL48AA, United Kingdom
%        {\tt\small firstname.surname@plymouth.ac.uk}}%
%}

\author{[Hidden for review]}
\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{xxx}
%  \streetaddress{xxx}
%  \city{Dublin} 
%  \state{Ohio} 
%  \postcode{43017-6221}
%}
%\email{trovato@corporation.com}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010520.10010553.10010554</concept_id>
<concept_desc>Computer systems organization~Robotics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Robotics}

\keywords{Human-Robot Interaction, Situation Assessment, Perspective Taking}

@@

@@

\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}
